Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-06 paper/paper_acm.tex
refactoring of introduction
rework plan of the paper

Nevertheless, the adaptation of the sheafification in higher topos
theory to homotopy type theory is not straightforward because the
construction in higher toposes is restricted to the initial Grothendieck
setting which is still very topologically oriented, and not very
amenable to formalization in type theory. It seems more promising to
use a generalized notion of sheafification, called Lawvere-Tierney
sheafification~\cite{tierney1972sheaf,maclanemoerdijk}
(LT-sheafification), but this construction has not
been considered yet in the setting of higher topos theory. This rises
two issues that this paper addresses: (i) how to lift the notion of
LT-sheafification to a higher dimensional setting and (ii) is it
possible to formalize this new definition in homotopy type theory.

@@

@@

In order to understand the construction of LT-sheafification in homotopy
type theory, we first briefly recall its corresponding construction in
topos theory.

@@

The work on forcing in type theory~\cite{jaber2012extending} also
gives a computational meaning to a type theory enriched with new
logical or computational principle, but for other kinds of principles
as the ones interpreted by LT-sheafification.
%
Actually, forcing is entirely complementary to LT-sheafification as
forcing corresponds to the presheaf construction while
LT-sheafification corresponds to the topological transformation that
allows to go from the presheaf to the sheaf construction.

Section~\ref{sec:hott} presents the foundations of homotopy type theory
and present a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
LT-sheafification functor.
%
The definitions of this paper uses an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

>>>>

Nevertheless, the adaptation of the sheafification process in higher
topos theory to homotopy type theory is not straightforward because
the construction in higher toposes is restricted to the initial
Grothendieck setting which is still very topologically oriented, and
not very amenable to formalization in type theory. It seems more
promising to use a generalized notion of sheafification, called
Lawvere-Tierney sheafification~\cite{tierney1972sheaf,maclanemoerdijk}
(LT-sheafification), but this construction has not been considered yet
in the setting of higher topos theory. This rises two issues that this
paper addresses: (i) how to lift the notion of LT-sheafification to a
higher dimensional setting and (ii) is it possible to formalize this
new definition in homotopy type theory.

@@

The work on forcing in type theory~\cite{jaber2012extending} also
gives a computational meaning to a type theory enriched with new
logical or computational principle, but for other kinds of principles
as the ones interpreted by LT-sheafification.
%
Actually, forcing is entirely complementary to LT-sheafification as
forcing corresponds to the presheaf construction while
LT-sheafification corresponds to the topological transformation that
allows to go from the presheaf construction to the sheaf construction.

Section~\ref{sec:lawv-tiern-nutshell} presents an overview of the
construction.
% 
Section~\ref{sec:hott} presents the foundations of homotopy type theory
and presents a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
LT-sheafification functor.
%
The definitions of this paper use an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:extension-type} describes how to use this
construction to define a modality on $\Type$ from a modality on
$\HProp$.
%
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

\section{Lawvere-Tierney Sheafification in a nutshell}
\label{sec:lawv-tiern-nutshell}

In order to understand the construction of LT-sheafification in homotopy
type theory, we first briefly recall the corresponding construction in
topos theory and then gives an overview of our construction.

@@

@@

@@

\nt{Add something on the definition of a syntactic translation as it
  has been done for forcing.}
